|

### 2025-01-29 doc/paper.qmd
prep filter

If a firm has missing values for any of the Earnings Per Share Report Date fields (`item5901`–`item5904`), it does not meet the criteria set by @ball_how_2008 and was excluded from the sample.

>>>>

If a firm had missing values for any of the Earnings Per Share Report Date fields (item5901–item5904), it did not meet the criteria set by @ball_how_2008 and was excluded from the sample. This filtering step removed 3,609,492 firm-year observations. Additionally, 5,996,793 firm-year entries were dropped because their four earnings announcements did not fall within the same calendar year. The final dataset consists of only 643,452 valid firm-year observations, starting in 1996 only, signaling the potential difference in the acocunting standards between the U.S. and Canada.
